First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2016-09-19 NIM/EG6_RTPC_NIM.tex
update the NIM writing and cleaning the directory

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He remains intact and recoils as a whole in the final state. The 
CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for similar 
studies on proton targets, however it cannot track recoils with momenta less 
than 250 MeV/c. In 2009, we carried out measurements on $^4$He target using
CLAS spectrometer, which was upgraded with a RTPC. The detector was positioned 
directly around the gaseous target, allowing a detection threshold of $~$125  
MeV/c for $^4$He. This article discuses the design of our RTPC, the methods we 
developed to calibrate it and its performances.
\end{abstract}

@@

The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF) in 
Newport News, Virginia, USA. The spectrometer is measuring charged particles as 
well as photons. The accelerator of the TJNAF provides a high power electron 
beam of energy up to 6 GeV and 100$\%$ duty cycle to the hall. The RTPC 
mentioned in this article has been used during a three months experimental run 
in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV sent 
on a gaseous helium-4 target to measure asymmetries in Deep Virtual Compton 
Scattering (DVCS)~\cite{proposal} and exclusive meson production (Meson Spec 
Prop). In these experiments, CLAS detects the high energy charged particles and 
the final real photon, for the latter the coverage has been extended using the 
optional inner calorimeter (ref).

\begin{figure}[h]
\centering 
\includegraphics[scale=0.3]{fig/test_clas.png}
\caption{\small\sf Three dimensional representation of the primary CLAS setup represents the geometry and the relative position of each subsystem. From outside, the electromagnetic calorimeter (green), time-of-flight system (red), Cherenkov counters (purple), three drift chamber regions (blue) and the superconducting torus coils (yellow).} 
\label{fig:CLAS}
\end{figure}

CLAS is composed of several subdetectors and two magnets. They are designed to track charged particles at momentum greater than 250 MeV/c. Figure~\ref{fig:CLAS} shows the basic setup of CLAS, ordered with respect to their radial distance from the center:

@@

In addition to the normal CLAS setup, a forward electromagnetic calorimeter (the inner calorimeter) was installed to improve the photon detection acceptance. Moreover, a 5~T solenoid was placed around the target to shield the detectors close to the beam line -- mostly the inner calorimeter and the RTPC -- from Mollers electrons. The solenoid field is also used to calculate the momentum of the alpha particles from their curvature radius measured by the RTPC.

The first implementation of a RTPC in CLAS have been achieved for the BoNuS experiment~\cite{BONUS} in 200x. The success of this detector for the detection of slow protons motivated the development of this new RTPC. For the channel of interests of our experiments, the recoiled $^{4}He$ nuclei have momentum around (150 or 300 ???) MeV/c, the detection of these particles was the primary motivation for using such design.

This paper is organized in this way: section \ref{sec_design} details the design and the internal structure of the RTPC, while section \ref{sec_readout} points the properties of the readout system. The calibration strategies for such detectors will be discussed in section \ref{sec_calib}. Finally, performances are discussed in section \ref{sec_perf}.

\section{Design} \label{sec_design}

The RTPC is a 200~mm long with a 150~mm diameter time projection chamber. The ionized electrons are drifting outward perpendicularly to the beam direction. These electrons are then amplified by three layers of GEMs and detected on 4.45 by 5~mm pads. As for BoNuS, the RTPC has two detection parts but unlike BoNuS they are part of a single chamber. Each part has independent GEM amplification systems that cover around 80\% of the azimuthal angle. Under the effect of the electromagnetic field, the ionization electrons drift to the readout system on the external shell with a curved trajectory as can be seen in the figure~\ref{fig:RTPC_1_4}.

@@

As seen in figure~\ref{fig:RTPC2}, the RTPC is composed from the beam axis to the exterior by:\\
\begin{itemize}
\item The target, filled with 5~atm $^4$He, has a 3~mm radius with Kapton walls only 27$\mu$m thick.
\item The first gas gap extends from 3 mm to 20 mm radial distance. It is filled with $^{4}He$ gas at 1~atm. During run, this region is swarmed by Moller electrons induced by the beam, such that filling this region with a light gas like $^{4}He$ minimizes secondary interactions. This region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar and connected to ground. 
\item The gap region extends between 20~mm and 30~mm and is filled with a gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME). This region is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which serves as the cathode.
\item The drift region is filled with the Ne-DME gas mixture, it extends from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away from the central axis. The electric field in this region is around 500~V/cm (???) and perpendicular to the beam. Field cages are installed at both ends of the detector in this region. Progressive voltage depending on radial position is applied on these to maintain a uniform electric field perpendicular to the beam line at the edges of the RTPC.
\item The GEM system is composed of three GEMs located at radii, 60 mm, 63 mm and 66 mm, they amplify the electrons to make a measurable signal.
\item The readout board has internal radius of 69~mm and collects the charges, preamplifiers are plugged directly on its outer side and are transmitting the signal to the data acquisition electronics.
\end{itemize}
\begin{figure}[tb]
\centering
\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
\caption[]{\small\sf A schematic layout of the GEMs system in one module of the RTPC.} 
\label{fig:GEMs}
\end{figure}

@@

\section{Readout System} \label{sec_readout}
The RTPC electron collecting system has 3200 readout pads. These collection elements are located at the end of the amplification region, 69 mm from the central axis.
\begin{figure}[tb]
\centering
%\hspace{-1 cm}
\includegraphics[scale=0.55]{fig/PADs.png}
\caption[]{\small\sf A schematic representation of a part of the readout system. The shaded sixteen pads are a group of pads that are connected to the same pre-amplifier.} 
\label{fig:PADs}
\end{figure}
Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in width the shift between the rows allows to reduce aliasing. Each half of the RTPC has 40 rows and 40 columns of pads. The shaded region in the figure~\ref{fig:PADs} shows how pads are grouped to the 16 channels pre-amplifiers. The Time to Digital Converter (TDC) units are 114~ns and indicates the time taken by the electron to drift from the ionization point to the readout board. On the the other side, the charge information is measured in Analog-to-Digital-Converter (ADC) units without specific normalization.

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.35]{fig/B_MAP.png}
\caption[]{\small\sf Schematic draw in of the solenoid magnetic vectors inside the RTPC. In this draw, r is the radial distance from the target's axis and z is the longitudinal position along the RTPC with its center at zero.} 
\label{fig:B_MAP}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.40]{fig/TDC_profile.png}
\caption[]{\small\sf Time profile of the collected hits in one experimental run. } 
\label{fig:TDC_profile}
\end{figure}

@@

\bibitem{CLASref}
B.A. Mecking et al., "The CEBAF large acceptance spectrometer", Nucl. Inst. and Meth. A 503, 513 (2003).

\bibitem{proposal}
K.Hafidi et al., "Deeply virtual Comton scattering off 4He", Jlab proposal to PAC33 (2007).
\bibitem{DCref}
M.D. Mestayer et al., "The CLAS drift chamber System", Nucl. Inst. and Meth. A 449, 81 (2000)

\bibitem{CCref}
G. Adams et al., "The CLAS Cerenkov detector", Nucl. Inst. and Meth. A 465, 414 (2001).

\bibitem{TOFref}E.S. Smith et al., "The time-of-flight system for CLAS", Nucl. Inst. and Meth. A 432, 265 (1999).

\bibitem{ECref}
M. Amarian et al., "The CLAS forward electromagnetic calorimeter", Nucl. Inst. and Meth. A 460, 239 (2001).

\bibitem{BONUS}
S. Tkachenko et al., "Measurement of the nearly free neutron structure function using spectator tagging in inelastic $^{2}H(e,e'p)X$ scattering with CLAS",	Phys. Rev. C 89, 045206 (2014).

\bibitem{MAGBOLTZ}
S. Biagi, "Monte Carlo simulation of electron drift and diffusion in counting gases under the influence of electric and magnetic fields", Nucl. Inst. and Meth. in Phy. Res. A, vol. 421, pp. 234-240, 1999.

>>>>

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He nucleus remains intact and recoils as a whole in the final 
state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
similar studies on proton targets, however it cannot track recoils with momenta 
less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
using CLAS spectrometer, which was upgraded with the RTPC. The detector was 
positioned directly around the gaseous target, allowing a detection threshold 
of $~$125  MeV/c for $^4$He. This article discuses the RTPC design, work 
principle, developed calibration methods and detector performance.
\end{abstract}

@@

The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF), 
Newport News, Virginia, USA. The accelerator of TJNAF provides a high power 
electron beam of energy up to 6 GeV and 100$\%$ duty cycle to three 
experimental Halls (A, B, C). The CLAS spectrometer is composed of several 
sub-detectors and two magnets. The spectrometer was designed to track charged 
particles at momentum greater than 250 MeV/c as well as detecting real photons.  
Figure~\ref{fig:CLAS} shows CLAS detector, ordered with respect to their radial 
distance from the center as:

@@

\begin{figure}[tbp]
\centering \includegraphics[scale=0.3]{fig/test_clas.png}
\caption{Three dimensional representation of the primary CLAS setup represents 
   the geometry and the relative position of each subsystem. From outside, the 
electromagnetic calorimeter (green), time-of-flight system (red), Cherenkov 
counters (purple), three drift chamber regions (blue) and the superconducting 
torus coils (yellow).} 
\label{fig:CLAS}
\end{figure}

In the basic setup of CLAS, the real photons are detected by the forward EC, 
covering polar angles from 8$^{\circ}$ to 45$^{\circ}$. With a 6 GeV electron 
beam, a large part of the DVCS photons are produced at polar angles below 
15$^{\circ}$, where the acceptance of the EC is small. In the CLAS-E1DVCS 
experiment (2005), CLAS was upgraded with the addition of an Inner Calorimeter 
(IC). This calorimeter covers polar angles between 5$^{\circ}$ and 
15$^{\circ}$. The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) 
crystals. Each crystal is 16 cm long (corresponding to 17 radiation lengths) 
with a 1.33~$\times$~1.33 cm$^2$ front surface and a 1.6~$\times$~1.6 cm$^2$ 
back surface. The energy resolution is around 3 to 4$\%$ for photon energies 
between 2 GeV and 5 GeV and the angular resolution is between 3 to 5 mrad for 
the same energy range \cite{Hyon-suk}.

The developed RTPC has been used during a three months experimental run in 2009 
with a longitudinally polarized electron beam of energy 6.064 GeV projected 
onto a gaseous $^{4}$He target to measure asymmetries in Deep Virtual Compton 
Scattering (DVCS)~\cite{proposal} and exclusive meson production. Moreover, a 
5~T solenoid was placed around the RTPC-target system to shield the detectors 
close to the beam line from Mollers electrons. The solenoid field plays also a 
major rule in finding the momentum of the charged particles in the RTPC by 
bending their tracks curvature.

This paper is organized in this way: section \ref{prev_tpc} presents an 
overview of the TPCs history and previous usage, section \ref{sec_design} 
details the physics considerations for the RTPC design and its internal 
structure, while section \ref{sec_readout} points the properties of the 
read-out system.  The calibration strategies for such detectors will be 
discussed in section \ref{sec_calib}. Finally, the performance of the RTPC is 
discussed in section \ref{sec_perf}.

\section{TPCs overview}
In the late 1970s, David R. Nygren presented the concept of the Time projection 
Chambers (TPCs) as a new tool to track charged particles based on combining 
electric and magnetic fields within a sensitive gas volume. The ionized 
electrons are collected by a position-sensitive electron collection system.  
Later in 1997, F.~Sauli introduced the Gas Electron Multiplier (GEM) as an 
effective gas-gain element to improve the tracking efficiency of the TPCs 
\ref{gem_sauli}.

The first implementation of a RTPC in CLAS have been achieved for the BoNuS 
experiment~\cite{BONUS} in 200x. The success of this detector for the detection 
of slow protons motivated the development of this new RTPC. For the channel of 
interests of our experiments, the recoiled $^{4}He$ nuclei have momentum per 
charge around 150 MeV/c, the detection of these particles was the primary 
motivation for using such design.

\section{CLAS-EG6 RTPC design} \label{sec_design}
The RTPC is a 200~mm long with a 150~mm diameter time projection chamber. The 
ionized electrons are drifting outward perpendicularly to the beam direction.  
These electrons are then amplified by three layers of GEMs and detected on 4.45 
by 5~mm pads. As for BoNuS, the RTPC has two detection parts but unlike BoNuS 
they are part of a single chamber. Each part has independent GEM amplification 
systems that cover around 80\% of the azimuthal angle. Under the effect of the 
electromagnetic field, the ionization electrons drift to the readout system on 
the external shell with a curved trajectory as can be seen in the 
figure~\ref{fig:RTPC_1_4}.

@@

As seen in figure~\ref{fig:RTPC2}, the RTPC is composed from the beam axis to 
the exterior by:\\
\begin{itemize}
   \item The target, filled with 5~atm $^4$He, has a 3~mm radius with Kapton 
      walls only 27$\mu$m thick.

   \item The first gas gap extends from 3 mm to 20 mm radial distance. It is 
   filled with $^{4}He$ gas at 1~atm. During run, this region is swarmed by 
   Moller electrons induced by the beam, such that filling this region with a 
   light gas like $^{4}He$ minimizes secondary interactions. This region is 
   surrounded by a 4 $\mu$m thick window made of aluminized Mylar and connected 
to ground.

   \item The gap region extends between 20~mm and 30~mm and is filled with a 
      gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME).  This region 
      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
      serves as the cathode.

   \item The drift region is filled with the Ne-DME gas mixture, it extends 
      from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
      from the central axis. The electric field in this region is around 
      500~V/cm (???) and perpendicular to the beam. Field cages are installed 
      at both ends of the detector in this region. Progressive voltage 
      depending on radial position is applied on these to maintain a uniform 
      electric field perpendicular to the beam line at the edges of the RTPC.

   \item The GEM system is composed of three GEMs located at radii, 60 mm, 63 
      mm and 66 mm, they amplify the electrons to make a measurable signal.

   \item The readout board has internal radius of 69~mm and collects the 
      charges, preamplifiers are plugged directly on its outer side and are 
      transmitting the signal to the data acquisition electronics.
\end{itemize}
\begin{figure}[tb]
\centering
\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
\caption[]{A schematic layout of the GEMs system in one module of the RTPC.} 
\label{fig:GEMs}
\end{figure}

@@

\section{Readout System} \label{sec_readout}
The RTPC electron collecting system has 3200 readout pads. These collection 
elements are located at the end of the amplification region, 69 mm from the 
central axis.

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.55]{fig/PADs.png}
   \caption[]{A schematic representation of a part of the readout system.  The 
   shaded sixteen pads are a group of pads that are connected to the same 
pre-amplifier.} \label{fig:PADs}
\end{figure}

Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment 
configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
width the shift between the rows allows to reduce aliasing. Each half of the 
RTPC has 40 rows and 40 columns of pads. The shaded region in the 
figure~\ref{fig:PADs} shows how pads are grouped to the 16 channels 
pre-amplifiers. The Time to Digital Converter (TDC) units are 114~ns and 
indicates the time taken by the electron to drift from the ionization point to 
the readout board. On the the other side, the charge information is measured in 
Analog-to-Digital-Converter (ADC) units without specific normalization.

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.35]{fig/B_MAP.png}
   \caption[]{Schematic draw in of the solenoid magnetic vectors inside the 
   RTPC. In this draw, r is the radial distance from the target's axis and z is 
the longitudinal position along the RTPC with its center at zero.} 
\label{fig:B_MAP}
\end{figure}

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.40]{fig/TDC_profile.png}
   \caption[]{Time profile of the collected hits in one experimental run.  } 
   \label{fig:TDC_profile}
\end{figure}

@@

\bibitem{CLASref}
   B.A. Mecking et al., The CEBAF large acceptance spectrometer, Nucl. Inst. 
   and Meth. A 503, 513 (2003).

\bibitem{proposal}
   K.Hafidi et al., Deeply virtual Comton scattering off $^{4}$He, Jlab 
   proposal to PAC33 (2007).

\bibitem{DCref}
   M.D. Mestayer et al., The CLAS drift chamber System, Nucl. Inst.  and Meth.  
   A 449, 81 (2000).

\bibitem{CCref}
   G. Adams et al., The CLAS Cerenkov detector", Nucl. Inst. and Meth. A 465, 
   414 (2001).

\bibitem{TOFref}
   E.S. Smith et al., The time-of-flight system for CLAS, Nucl.  Inst. and 
   Meth. A 432, 265 (1999).

\bibitem{ECref}
   M. Amarian et al., The CLAS forward electromagnetic calorimeter, Nucl.  
   Inst. and Meth. A 460, 239 (2001).

\bibitem{Hyon-suk}
   Hyon-Suk Jo, Etude de la Diffusion Compton Profond{\'e}ment Virtuelle Sur le 
   Nucl{\'e}on avec le D{\'e}tecteur CLAS de Jefferson Lab: Mesure des Sections 
   Efficaces polaris{\'e}es et non polaris{\'e}es, IPNO-Thesis, 2007.

\bibitem{gem_sauli}
   F. Sauli, GEM: A new concept for electron amplification in gas detectors, 
   Nucl. Instr. and Meth. A 386, 531 (1997).

\bibitem{BONUS}
   S. Tkachenko et al., Measurement of the nearly free neutron structure 
   function using spectator tagging in inelastic $^{2}H(e,e'p)X$ scattering 
   with CLAS,	Phys. Rev. C 89, 045206 (2014).

\bibitem{MAGBOLTZ}
   S. Biagi, Monte Carlo simulation of electron drift and diffusion in counting 
   gases under the influence of electric and magnetic fields, Nucl.  Inst. and 
   Meth. in Phy. Res. A, vol. 421, pp. 234-240, 1999.

### 2016-09-19 coherent/HeliumCohDVCS.tex
update the NIM writing and cleaning the directory

\begin{abstract}
We report the first exclusive measurement of deeply virtual Compton scatterring 
(DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
observed beam spin asymmetries are significantly larger than for proton, 
confirming expectations from plane wave impulse approximation. We present an 
extraction of the unique generalized parton distribution (GPD) of the spin-0 
helium in a completely model independent way. This result demonstrate the 
strength of the method and opens a new unique access into nuclei 3D structure 
in term of quarks and gluons.
\end{abstract}

@@

The generalized parton distribution (GPD) framework developped in the past two decades
(Need a bunch of refs)~\cite{}
offers a unique access into hadron 3D structure through deeply virtual Compton
scattering (DVCS), depicted in figure~\ref{fig:DVCS} and other exclusive processes. Many measurements on the proton
at several energies have now be reported and have demonstrated the solidity of the
method~\cite{}. %To enhance a little -> CFF

Insert FIGURE DVCS nuclei
%\label{fig:DVCS}
\begin{figure}[htbp]
\caption{\label{fig:DVCS} Coherent DVCS}
\includegraphics[width=8.6cm]{DVCS.png}
\end{figure}

At the same time, the partonic structure of nuclei has remained a mystery
for the past three decades, as we are still unable to explain properly the 
infamous EMC effect~\cite{}. First observed in 197X by the EMC 
collaboration, it describes the difference between the partonic structure of
free and bound nucleons. Understanding the source of this difference remains 
today a topic of active research~\cite{},
questionning our understanding of nuclei and their structure beyond protons
and neutrons~\cite{}. As studies based on inclusive measurements of the
effect seem to be too limited to tackle the question definitively, we can now
apply the GPD framework to study the nuclei in three dimensions and observe
the EMC effect in an unprecedented way.
%Elaborate on non nucleonic degrees of freedom and other interests of He DVCS

The measurement of DVCS on helium 4 is in this regard the perfect experiment for
several reasons. First, Helium 4 is of spin-0, such that a single GPD ($H$) is
necessary for the description of the DVCS at leading order. This feature allows for a
completely model independant extraction of the CFF from data that is impossible for 
protons and neutrons which need 4 GPDs, leading to complex underconstrained 
problems~\cite{}. Second, helium 4, while a small nuclei, is dense and experience 
already a significant EMC effect, while being simple enough that its nuclear
structure is very well known~\cite{} (Low energy struct, FF,...). Third, being 
light enough helium 4 can exit
a light target and be experimentally measured, insuring the exclusivity of the 
measurement. This point is especially important as we are probing with a 
multi-GeV interaction a nuclei bound by only a few MeV, this leads in the 
overwhelming majority of the cases to the incoherent break-up of the target.

%\section{Experiment}
The HERMES collaboration has measured nuclear DVCS~\cite{} without the 
possibility of separating the coherent and incoherent channels leading
to controversy in the interpretation of their results~\cite{}. We report
here our measurement of coherent DVCS off helium-4 at the Jefferson labortory
(JLab), while our results for the incoherent channel will be presented in
another paper~\cite{}. This experimental facility delivers a nearly 100\% duty factor, 6~GeV 
electron linear accelerator into three experimental halls. Our experiment
ran for 3 months in 2009 using the CEBAF Large Acceptance Spectrometer (CLAS).
This detector is covering about 2$\pi$ and is composed of drift chambers, Cherenkov counters, scintillator 
counters and an electro-magnetic calorimeter. It allows to detect accurately
electrons and provides a trigger for the experiment. It is complemented for DVCS experiments with
an inner calorimeter to detect the photons emitted at low angle and a solenoid
to keep the Moller electrons produced along the beam line to get into our detectors.

In order to insure the coherence of the process, we detect all the products
of the reaction. The electron is detected by the CLAS, using the drift chamber 
to reconstruct its trajectory and the combination of the Cherenkov counters
and electromagnetic calorimeter to

we built a small and light 
radial time projection chamber (RTPC) depicted in figure~\ref{fig:rtpc} to 
detect the recoiling helium nuclei. this detector is placed directly ouside of 
our gaseous target filled with 6~atm helium. 
% to complete

\begin{figure}[htbp]
\caption{\label{fig:rtpc} RTPC description}
\includegraphics[width=8cm]{RTPC.png}
\end{figure}

@@

Detection, PID des particules.

\begin{figure*}[htbp]
\caption{\label{fig:exclu} Exclusivity cuts}
\includegraphics[width=17.2cm]{all_coh_exc_cuts.png}
\end{figure*}

We identified several background contributions to the DVCS process, in 
particular accidental events and exclusive deeply virtual $\pi^0$ production (DV$\pi^0$P). The accidental
events happen when an helium nuclei is mistakenly associated with our event, this 
possibility is suppressed by the limited phase space allowed but enhanced by the
low time resolution of the RTPC (~200 ns). We evaluated this contribution by
selecting events passing all our cuts but with particles originating from 
different verteces. With this method, we found this background to represent 
4.1\%. The DV$\pi^0$P events can easily be mistaken
with DVCS events when one of the two photons of $\pi^0$ decay is produced at
low energy in the laboratory frame. In order to estimate the importance of
this background, we developped an event generator DV$\pi^0$P 
that we calibrated to match our experimental yields. We used this generator together 
with a GEANT3~\cite{} simulation of our detection system to estimate the ratio 
of acceptance between measured DV$\pi^0$P and DV$\pi^0$P that would pass our 
DVCS selection cuts. This ratio obtained from simulation is then multiplied by 
the measured yield of DV$\pi^0$P events, indicating a contamination of XX to XX\%. 
%(We NEED a figure of that in the note!!!)

>>>>

\begin{abstract}
We report the first exclusive measurement of deeply virtual Compton scattering 
(DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
observed beam spin asymmetries are significantly larger than for proton, 
confirming expectations from calculations using the plane wave impulse 
approximation. We present an 
extraction of the single generalized parton distribution (GPD) of the spin-0 
helium-4 nuclei in a completely model independent way. This result demonstrate the 
strength of the method and opens a new and unique access into the partonic structure 
of nuclei.
\end{abstract}

@@

The generalized parton distribution (GPD) framework developped in the past 
two decades~\cite{}
offers a unique access into hadron 3D structure through deeply virtual Compton
scattering (DVCS), depicted in figure~\ref{fig:DVCS}, and other exclusive 
processes. Many measurements on the proton
at several energies have now be reported~\cite{} and phenomenological work
have demonstrated the solidity of the method to extract the tomography of the
nucleon from these data~\cite{}.

\begin{figure}[htbp]
\caption{\label{fig:DVCS} Diagram for the coherent DVCS in the plane wave approximation.}
\includegraphics[width=8.6cm]{DVCS.png}
\end{figure}

At the same time, the partonic structure of nuclei has remained a mystery
for the past three decades, as we are still unable to explain properly the 
infamous EMC effect~\cite{}. First observed in 197X by the EMC 
collaboration, it describes the difference between the partonic structure of
free and bound nucleons. Understanding the source of this difference remains 
today a topic of active research~\cite{},
questionning the basics of our understanding of nuclei and their 
structure~\cite{}. Studies based on inclusive measurements of the
effect provide a very detailed description~\cite{} but 
are still unable to tackle the question definitively. Therefore,
using the GPD framework and exclusive channels to study the nuclei in three 
dimensions will give completely new information that will affect our understanding
of the EMC effect in an unprecedented way~\cite{}. 
%In particular, the GPDs 
%allow to isolate the components of the nuclei which are not nucleonic~\cite{}.

The measurement of DVCS on helium-4 is in this regard the perfect experiment for
several reasons. First, Helium 4 is of spin-0, such that a single GPD ($H$) is
necessary for the description of the DVCS at leading order. This feature allows for a
completely model independant extraction of the CFF from data that is impossible for 
protons and neutrons which have 4 GPDs~\cite{}. Second, 
helium 4 is dense and experience 
already a significant EMC effect, while being simple enough that its nuclear
structure is well known~\cite{}. Third, being 
light enough helium-4 can exit
a light target and be experimentally measured in a coherent DVCS process, 
insuring the exclusivity of the 
measurement. This point is especially important because we are probing with a 
multi-GeV interaction a nuclei bound by only a few MeV, this leads in the 
overwhelming majority of the cases to the incoherent break-up of the target.

%\section{Experiment}
The HERMES collaboration has measured nuclear DVCS~\cite{} without the 
detection of the recoils separating the coherent and incoherent channels 
based on the measurement of the transfered 4-momentum $t$, leading
to controversy in the interpretation of their results~\cite{}. We report
here our exclusive measurement of coherent DVCS off helium-4 at the Jefferson labortory
(JLab), while our results for the incoherent channel will be presented in
another paper. JLab delivers a nearly 100\% duty factor, 6~GeV linearly 
polarized electrons into three experimental halls. Our experiment ran for 3 
months in 2009 using the CEBAF Large Acceptance Spectrometer (CLAS) in 
Hall-B. This detector is large acceptance covering nearly 2$\pi$ and is 
composed of drift chambers, Cherenkov counters, scintillator counters and 
an electro-magnetic calorimeter. It allows to detect accurately electrons 
which provide the trigger for the experiment. It is complemented for DVCS 
experiments with an inner electro-magnetic calorimeter made of PbWO crystals 
to detect the photons emitted at low angle and with a solenoid to keep the 
Moller electrons produced along the beam line to get into our detectors.

In order to ensure the coherence of the process, we also detect the recoiling 
helium-4 nuclei. We built a small and light radial time projection chamber 
(RTPC) to detect recoiling helium nuclei down to energies of few MeVs. The 
chamber, shown in figure~\ref{fig:rtpc}, is surrounding the gaseous target 
filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial drift 
length. The detector was specifically calibrated for helium-4 nuclei using 
elastic scattering produced with a 1.2~GeV electron beam.
To ensure that the process is exclusive, we apply cuts on 
several kinematic variables (figure~\ref{fig:exclu}) such as missing energy,
mass and momentum. The cuts are chosen to represent consistently 3 half width 
at half maximum in order to avoid any bias in the selection.

@@

\begin{figure}[tb!]
\caption{\label{fig:rtpc} RTPC description}
\includegraphics[width=7.4cm]{RTPC.png}
\end{figure}

\begin{figure*}[t!]
\caption{\label{fig:exclu} Exclusivity cuts}
\includegraphics[width=16.0cm]{all_coh_exc_cuts.png}
\end{figure*}

We identified several background contributions to the DVCS process, in 
particular accidental events and exclusive deeply virtual 
$\pi^0$ production (DV$\pi^0$P). The accidental
events where the different particles come from different events are 
suppressed by the limited phase space allowed by the exclusivity cuts. We 
estimate the accidental events to represent 4.1\% of our sample. This relatively 
large number is due to the small cross section of the DVCS. We evaluated this contribution by
selecting events passing all our cuts but with particles originating from 
different verteces.

Another important source of background is the deeply virtual 
$\pi^0$ production (DV$\pi^0$P), which can easily be mistaken
with DVCS when one of the two photons of the $\pi^0$ decay is produced at
low energy in the laboratory frame. To estimate the importance of
this background, we developped an event generator 
that we calibrated to match our measured experimental yield of exclusive 
$pi^0$. We used this generator together 
with a GEANT3 simulation of our detection system to estimate the ratio 
of acceptance between DV$\pi^0$P where the two photons are detected and those
where only one photon is detected and would pass our 
DVCS selection cuts. This ratio obtained from simulation is then multiplied by 
the measured yield of DV$\pi^0$P events, indicating a contamination of 2 to 4\%.
